---
title: "Bus Ridership Analysis"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

#### Create a vector s1 whose elements correspond to the number of passengers who can possibly get on board the bus at a particular stop.
```{r}
s1 = c(0,1,2)
```

####Create a vector p1 whose elements correspond to the respective chances of the number of
passengers identified in the previous question getting on board the bus at a particular stop.
```{r}
p1 = c(0.5,0.4,0.1)
```

####Create a matrix P such that the jth column of this matrix should have a passenger on the
bus’s continuing-on and getting-off chances for the jth stop for j = 1, . . . , 10.
```{r}
P = matrix(c(0.99, 0.01, 0.2, 0.8, 0.2, 0.8, 0.8, 0.2, 0.8, 0.2, 0.8, 0.2, 0.8, 0.2, 0.2,0.8, 0.2, 0.8, 0.0,1.0),nrow = 2 , ncol = 10)
P
```
#### Create a 2-vector s2 whose elements correspond to the encoded versions of a passenger staying on the bus and getting off of the bus at a particular stop, respectively.
```{r}

s2 = c(0,1)
```

#Getting a sample size 
```{r}
sample(s1, size = 10, replace = T, prob = p1)
```

####Explain what the following R code helps us achieve in reference to the bus-ridership process:


```{r}

n = 30 # zero passengers in the bus at stop 1
for (j in 1:9){
  # simulating continuing or getting off of the bus 
  if (n > 0){ #  if there is at least one passengers in the bus
  n = n - sum(sample(s2, size = n, replace = TRUE, prob = P[, j])) #Simulating/Updating current passengers - the no of passengers getting off the bus at the j-th stop
  }
  # Update the current no of passenger in the bus  by adding the no of passengers that board the bus at the j-th stop
  n = n + sample(s1, size = 1, replace = FALSE, prob = p1)
  cat(sprintf("No of Passengers after the stop-%d = %d\n",j,n))
}

```

```{r}

table_a = paste0('A',c(1:10))
S1 = c('A1','A2')
S2 = c(paste0('A',c(3:10)),paste0('B',c(1:10)))
P1 = c(0.5,0.5)
P2 = replicate(18,1/18)
S1
S2
sample(S1,size=1,prob=P1)
sample(S2,size=1,prob=P2)
c(sample(S1,size=1,prob=P1),sample(S2,size=1,prob=P2))
c()
```


